---
title: "Homework 2 Codes"
author: "Group C-SAT"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#install.packages("readxl")
#install.packages("psych")
#install.packages("GGally")
library(Hmisc)
library(readxl)
library(psych)
library(GGally)
```


# Load the file
```{r 1}
rm(list = ls())
file <- read_excel("HW2_MultimediaHW.xlsx")
```


# Data Description

# How the data relate
```{r corr matrix before transformation}
cor(file[2:15])
```


# Data Description
```{r 2 DD}
describe(file)
```
# Explore variable correlation after sqrt tranformation
```{r corr matrox sqrt}
Sqcols = sqrt(file[3:15])
Newfile = cbind(file[2], Sqcols)
Hmisc::rcorr(as.matrix(Newfile))
```
## sqrt of ADV_online, Search, Portals are significantly correlates with dependent variable
## Strong multi-colinearity between several pairs such as Sqrt(Search) and Sqrt(Portals )

# Drop Banner and Social Media because all of values are zero

# Drop these variables that are xtremely skewed after transformation(because of a lot of zero values)
```{r}
hist(sqrt(file$Catalogs_Winback))
hist(sqrt(file$Catalogs_NewCust))
hist(sqrt(file$Mailings))
hist(sqrt(file$Retargeting))
```


#Get candidate variables
```{r Candidate var}
Sales = file$`Sales (units)`
Stm1 = Lag(Sales,shift=1)

SqADV_Total = sqrt(file$ADV_Total)
SqADV_Offline = sqrt(file$ADV_Offline)

SqCatEx = sqrt(file$Catalogs_ExistCust)


SqADV_online = sqrt(file$ADV_online)

SqSearch = sqrt(file$Search)

SqNL = sqrt(file$Newsletter)

SqPortals = sqrt(file$Portals)
```
## SqSearch SqPortals should only include one because of multicolinearity

# Histogram of candidate variables
```{r hist candidate vars sqrt}
hist(SqADV_Total)

hist(SqADV_Offline)
hist(SqCatEx)

hist(SqADV_online)
hist(SqSearch)
hist(SqPortals)
hist(SqNL)
```



# Main Model 1
```{r m1}
regmodm1<-lm(Sales~Stm1+SqADV_Total)
# test normality of residuals
res1 = resid(regmodm1)
hist(res1)
nortest::ad.test(res1)
```

```{r m1 result}
summary(regmodm1)
AIC(regmodm1)
BIC(regmodm1)
```
# Main Model 2
```{r m2}
regmodm2<-lm(Sales~Stm1+SqADV_Offline+SqADV_online)
res2 = resid(regmodm2)
hist(res2)
nortest::ad.test(res2)
```

```{r m2 result}
summary(regmodm2)
AIC(regmodm2)
BIC(regmodm2)
```



# Main Model 3
```{r m3 Search}
#Try Search
regmodS<-lm(Sales~Stm1+SqCatEx+SqSearch+SqNL)
summary(regmodS)
AIC(regmodS)
BIC(regmodS)
```

```{r m3 Portal}
#Try Portal
regmodP<-lm(Sales~Stm1+SqCatEx+SqPortals+SqNL)
summary(regmodP)
AIC(regmodP)
BIC(regmodP)
```

```{r m3 Combine}
SqCom = sqrt(file$Search+file$Portals)
regmodC<-lm(Sales~Stm1+SqCatEx+SqCom+SqNL)
summary(regmodC)
AIC(regmodC)
BIC(regmodC)
```

## Finally we choose Portal because it is the best(lowest AIC BIC)
```{r m3 Final}
regmodm3<-lm(Sales~Stm1+SqCatEx+SqPortals+SqNL)
summary(regmodm3)
AIC(regmodm3)
BIC(regmodm3)
```

```{r m3 test}
res3 = resid(regmodm3)
hist(res3)
nortest::ad.test(res3)
```


# Explore better model

## Log model provides better fit(higher r2 and adj-r2)
```{r m5 new}
LogADV_Total = log(file$ADV_Total+1)

LogADV_Offline = log(file$ADV_Offline+1)
LogCatEx = log(file$Catalogs_ExistCust+1)

LogADV_online = log(file$ADV_online+1)
LogSearch = log(file$Search+1)
LogPortals = log(file$Portals+1)  
LogNL = log(file$Newsletter+1)

regmodlog<-lm(Sales~Stm1+LogCatEx+LogPortals+LogNL)
summary(regmodlog)
AIC(regmodlog)
BIC(regmodlog)
```

# Without Lagging effect is a worse fit (higher AIC and BIC)
```{r no lagging}
regmodnl<-lm(Sales~SqCatEx+SqPortals+SqNL)
summary(regmodnl)
AIC(regmodnl)
BIC(regmodnl)
```

# Without intercept is a worse fit (higher AIC and BIC)
```{r withou intercept}
regmodni<-lm(Sales~Stm1+SqCatEx+SqPortals+SqNL-1)
summary(regmodni)
AIC(regmodni)
BIC(regmodni)
```
## R2 and Adj-R2 is so much higher, but AIC/BIC is higher as well.
## This means better explanatory ability but poorer predicability
## R2 always get approx 0.9 when taking intercept

# Explore synergy 
# Try sqrt model with synergy
```{r sqrt syn}
regmodss<-lm(Sales~Stm1+Sq+SqPortals+SqNL+SqCatEx*SqPortals+SqCatEx*SqNL)
summary(regmodss)
AIC(regmodss)
BIC(regmodss)
```
This model make most sense the

# Try AGG sqrt model with synergy
```{r sqrt syn}
regmodss<-lm(Sales~Stm1+SqADV_Offline+SqADV_online+SqADV_Offline*SqADV_online)
summary(regmodss)
AIC(regmodss)
BIC(regmodss)
```
# Try log model with synergy
```{r log syn}
regmodls<-lm(Sales~Stm1+LogCatEx+LogPortals+LogNL+LogCatEx*LogPortals+LogCatEx*LogNL)
summary(regmodls)
AIC(regmodls)
BIC(regmodls)
```

# Try log model with synergy
```{r log syn}
LogCatWB = log(file$Catalogs_Winback+1)
regmodls<-lm(Sales~Stm1+LogCatEx+LogCatWB+LogPortals+LogNL+LogCatEx*LogPortals+LogCatEx*LogNL+LogCatWB*LogPortals+LogCatWB*LogNL)
summary(regmodls)
AIC(regmodls)
BIC(regmodls)
```

# Try AGG log model without intercept and with synergy
```{r agg l ni s}
regmod<-lm(Sales~Stm1+LogADV_Offline+LogADV_online+LogADV_Offline*LogADV_online-1)
summary(regmod)
AIC(regmod)
BIC(regmod)
```

# Try AGG sqrt model without intercept and with synergy
```{r agg sqrt without intercept and with synergy}
regmod<-lm(Sales~Stm1+SqADV_Offline+SqADV_online+SqADV_Offline*SqADV_online-1)
summary(regmod)
AIC(regmod)
BIC(regmod)
```

# Try log model with synergy without intercept
```{r log syn ni}
regmodls<-lm(Sales~Stm1+LogCatEx+LogPortals+LogNL+LogCatEx*LogPortals+LogCatEx*LogNL-1)
summary(regmodls)
AIC(regmodls)
BIC(regmodls)
```

# Try sqrt model with synergy without intercept
```{r sqrt syn ni}
regmodss<-lm(Sales~Stm1+SqCatEx+SqPortals+SqNL+SqCatEx*SqPortals+SqCatEx*SqNL-1)
summary(regmodss)
AIC(regmodss)
BIC(regmodss)
```

# Try part log model with synergy 
```{r sqrt syn ni}
ADV_Total = file$ADV_Total
ADV_Offline = file$ADV_Offline
CatEx = file$Catalogs_ExistCust

ADV_online = file$ADV_online
NL = file$Newsletter
Portals = file$Portals

Search = file$Search


plot(Sales~CatEx)
plot(Sales~LogNL)
plot(Sales~Portals)
```

```{r sqrt syn ni}
regmodss<-lm(Sales~Stm1+CatEx+Portals+LogNL+CatEx*Portals+CatEx*LogNL)
summary(regmodss)
AIC(regmodss)
BIC(regmodss)
```